Efficient Handling of String-Number Conversion

### 2019-11-22 evaluation.tex
Add one paragraph to evaluation.

In the second experiment, we compare with tools supporting string-number conversion on the benchmarks collected from the symbolic executor \texttt{Py-Conbyte}\footnote{\url{https://github.com/spencerwuwu/py-conbyte}}, which has the supports of string-number conversion. We run it on several examples collected from the LeetCode platform and from Python core libraries. We also have examples that encode execution paths of some JavaScript programs (the Luhn algorithm and some array manipulation).

@@

\todo{Mention about (1) checkLuhn cases (2) out tool solves much more cases if timeout is set to 30s. (3) update table with data of timeout=30s}

\begin{table}[h]
\centering
\caption{Comparison of {\tool}, CVC4, and Z3/Z3str3 with checkLuhn problems of 2 to 12 loops.}
\scalebox{0.9}{
\begin{tabular}{| c | c c c c|}
\hline
\# of Loops & {\tool} 			   &  CVC4    	 		  &       Z3   			& Z3-str3 \\ \hline
2 			& \textbf{SAT}(<0.1s)  &  \textbf{SAT}(0.66s) & \textbf{SAT}(0.23s) & $\times$ \\
3  			& \textbf{SAT}(<0.1s)  &  \textbf{SAT}(1.78s) & \textbf{SAT}(0.13s) & $\times$ \\
4 			& \textbf{SAT}(<0.1s)  &  \textbf{SAT}(6.96s) &   $\times$  		& $\times$ \\
5 			& \textbf{SAT}(<0.1s)  &  \textbf{SAT}(17.2s) &   $\times$  		& $\times$ \\
6 			& \textbf{SAT}(0.16s)  &  $\times$  		  & \textbf{SAT}(0.14s) & $\times$ \\
7 			& \textbf{SAT}(0.24s)  &  $\times$    		  &   $\times$  		& $\times$ \\
8 			& \textbf{SAT}(0.31s)  &  $\times$   		  & \textbf{SAT}(0.37s) & $\times$ \\
9 			& \textbf{SAT}(0.26s)  &  $\times$    		  &   $\times$  		& $\times$ \\
10 			& \textbf{SAT}(0.21s)  &  $\times$    		  & \textbf{SAT}(0.62s) & $\times$ \\
11 			& \textbf{SAT}(0.23s)  &  $\times$    		  & \textbf{SAT}(0.47s) & $\times$ \\
12 			& \textbf{SAT}(0.33s)  &  $\times$     		  & \textbf{SAT}(0.47s) & $\times$ \\ \hline
\end{tabular}}
\label{table:checkLuhn}
\end{table}

@@

\hide{
\begin{figure}
\begin{tikzpicture}
\begin{axis}
\addplot+[sharp plot]
coordinates
{
(2,0.097)
(3,0.078)
(4,0.098)
(5,0.098)
(6,0.161)
(7,0.236)
(8,0.307)
(9,0.26)
(10,0.211)
(11,0.228)
(12,0.33)
};
\end{axis}
\end{tikzpicture}
\caption{checkLuhn: z3-trau}
\end{figure}

\begin{figure}
\begin{tikzpicture}
\begin{axis}
\addplot+[sharp plot]
coordinates
{
(2,0.266)
(3,10.084)
(4,48.791)
(5,120)
(6,120)
(7,120)
(8,120)
(9,120)
(10,120)
(11,120)
(12,120)
};
\end{axis}
\end{tikzpicture}
\caption{checkLuhn: cvc4 (SAT if not timeout)}
\end{figure}

\begin{figure}
\begin{tikzpicture}
\begin{axis}
\addplot+[sharp plot]
coordinates
{
(2,0.238)
(3,0.128)
(4,120)
(5,120)
(6,0.134)
(7,120)
(8,0.366)
(9,120)
(10,0.526)
(11,0.374)
(12,0.405)
};
\end{axis}
\end{tikzpicture}
\caption{checkLuhn: z3 (SAT if not timeout)}
\end{figure}

\begin{figure}
\begin{tikzpicture}
\begin{axis}
\addplot+[sharp plot]
coordinates
{
(2,0.4743)
(3,0.56052)
(4,0.36695)
(5,0.60905)
(6,22.06429)
(7,53.77536)
(8,118.41196)
(9,0.50559)
(10,120)
(11,0.42953)
(12,120)
};
\end{axis}
\end{tikzpicture}
\caption{checkLuhn: z3str3 (UNKNOWN if not timeout)}
\end{figure}
}

>>>>

In the second experiment, we compare with tools supporting string-number conversion on the benchmarks collected from the symbolic executor \texttt{Py-Conbyte}\footnote{\url{https://github.com/spencerwuwu/py-conbyte}}, which has the supports of string-number conversion. We ran it on several examples collected from the LeetCode platform and from Python core libraries. We also have examples that encode execution paths of some JavaScript programs (the Luhn algorithm and some array manipulation).

@@

To address the effectiveness of our PFA strategy, we also ran experiments on the String-Number Conversion benchmark with the the timeout set to 30s. Provided more time for solving, {\tool} managed to obtain more results and the timeout number is reduced to about 100, while other tools got almost the same number of timouts with the results of timeout set to 10s. Also, we have encoded the checkLuhn algorithm in SMT-lib for cases of 2 to 12 loops (digits). These problems ask for a model of a valid credit card number as a string of length 2 to 12 each case. We ran these tests additionally to the experiments above with the timeout set to 120s. In these tests, {\tool} can solve all 11 problems within 1s while CVC4 only returns a model for cases of 2 to 5 loops and Z3-str3 could not solve these problems (either timeout or UNKNOWN). However, Z3 can still solve 7 out of the 11 problems and the problems got timeout are cases for 4, 5, 7, and 9 loops. It seems that Z3 has some strategies that can solve problems of even loops efficiently. \todo{Update table with data of timeout=30s}

\hide{
\begin{table}[h]
\centering
\caption{Comparison of {\tool}, CVC4, and Z3/Z3str3 with checkLuhn problems of 2 to 12 loops.}
\scalebox{0.9}{
\begin{tabular}{| c | c c c c|}
\hline
\# of Loops & {\tool} 			   &  CVC4    	 		  &       Z3   			& Z3-str3 \\ \hline
2 			& \textbf{SAT}(<0.1s)  &  \textbf{SAT}(0.66s) & \textbf{SAT}(0.23s) & $\times$ \\
3  			& \textbf{SAT}(<0.1s)  &  \textbf{SAT}(1.78s) & \textbf{SAT}(0.13s) & $\times$ \\
4 			& \textbf{SAT}(<0.1s)  &  \textbf{SAT}(6.96s) &   $\times$  		& $\times$ \\
5 			& \textbf{SAT}(<0.1s)  &  \textbf{SAT}(17.2s) &   $\times$  		& $\times$ \\
6 			& \textbf{SAT}(0.16s)  &  $\times$  		  & \textbf{SAT}(0.14s) & $\times$ \\
7 			& \textbf{SAT}(0.24s)  &  $\times$    		  &   $\times$  		& $\times$ \\
8 			& \textbf{SAT}(0.31s)  &  $\times$   		  & \textbf{SAT}(0.37s) & $\times$ \\
9 			& \textbf{SAT}(0.26s)  &  $\times$    		  &   $\times$  		& $\times$ \\
10 			& \textbf{SAT}(0.21s)  &  $\times$    		  & \textbf{SAT}(0.62s) & $\times$ \\
11 			& \textbf{SAT}(0.23s)  &  $\times$    		  & \textbf{SAT}(0.47s) & $\times$ \\
12 			& \textbf{SAT}(0.33s)  &  $\times$     		  & \textbf{SAT}(0.47s) & $\times$ \\ \hline
\end{tabular}}
\label{table:checkLuhn}
\end{table}
}

@@
